\chapter{automata abstract}

$\emph{P}$ $\texttt{P}$ $\P$  $\mathrm{P}$  $\mathcal{P}$ $\mathit{P}$  $\mathnormal{P}$  $\boldsymbol{P}$  $\mathbf{P}$

\hfill

\section*{}
\cite[p6]{WATSON93a} $\textbf{the signatures of the transition relations:}$

$T \in \mathbb{P}(Q \times V \times Q)$

$T \in V \to P(Q \times Q)$

$T \in Q\times Q \to P(V)$

$T \in Q \times V \to P(Q)$

$T \in Q \to P(V \times Q)$

for example, the function $T \in Q \to P(V \times Q)$ is defined as $T(p) = \{(a,q):(p,a,q) \in T\}$

\hfill

$\textbf{$\epsilon$-transition relation:}$

$E \in P(Q\times Q)$

$E \in Q \to P(Q)$

\hfill

$T \in P(Q \times V \times Q), T = \{(s,a,q) \}$

$T(s)\in Q \to P(V\times Q), T(s) = \{(a,q):(s,a,q) \in T\}$

$Q_{map}: P(Q\times V), Q_{map} = \{(q,a): (s,a,q) \in T\}$

$Q_{map}(q) = \{a: (s,a,q)\in T\}$

${Q_{map}}^{-1}: V \nrightarrow P(Q), {Q_{map}}^{-1} = \{(a,q): (s,a,q) \in T\}$

According to \cite[Convention A.4]{WATSON93a} (Tuple projection):

$\bar{\pi}_2(T) = \{(s,q): (s,a,q)\in T \}$

$Q_{map} = (\bar{\pi}_1(T))^R, Q_{map} = \{(a,q):(s,a,q) \in T\}^R = \{(q,a):(s,a,q) \in T\}$

\hfill

$f(a)=(f(a^R))^R$

\hfill

\begin{definition}[Prefix-closure\cite{Chrison2007}]
	Let $L\subseteq V^*$,then
	$$\overline{L} := \{s\in V^*:(\exists t\in V^*)[st\in L]\}$$
\end{definition}
In words, the prefix closure of L is the language denoted by $\overline{L}$ and consisting of all the prefixes in L. In general, $L\subseteq \overline{L}$.

L is said to be prefix-closed if $L = \overline{L}$. Thus language L is prefix-closed if any prefix of any string in L is also an element of L.

$L_1 = \{\epsilon,a,aa\}, L_1 = \overline{L_1}, L_{1}$ is prefix-closed.

$L_2 = \{a,b,ab\}, \overline{L_2} = \{\epsilon,a,b,ab\}, L_2 \subset \overline{L_2}, L_2$ is not prefix closed.

\hfill

\begin{definition}[Post-closure\cite{Chrison2007}]
Let $L\subseteq V^{\ast}$ and $s\in L$. Then the post-language of L after s, denoted by L/s, is the language
$$ L/s := \{t\in V^{\ast}:st\in L\}$$
By definition, $L/s = \emptyset$ if $s \notin \overline{L}$.
\end{definition}

\hfill

\begin{definition}[Left derivatives\cite{WATSON93a}] Given language $A\subseteq V^{\ast}$ and $w\in V^{\ast}$ we define the left derivative of A with respect to $w$ as:
$$w^{-1}A = \{x\in V^{\ast}:wx\in A\}$$
$A$关于$w$的左导数，就是$A$中： \{$w$的后缀组成的字符串集合\}。

Sometimes derivatives are written as $D_{w}A$ or as $\frac{dA}{dw}$. Right derivatives are analogously defined. Derivatives can also be extended to $B^{-1}A$ where B is also a language.
\end{definition}

\begin{example}
$A = \{a,aab,baa\},a^{-1}A = D_{a}A = \frac{dA}{da} =\{\epsilon,ab,\emptyset\} = \{\epsilon,ab\}$ \hfill$\square$ 
\end{example}

\begin{example}
	$L = \{ba,baa,baab,ca\}, w = \{ba\},$
	
	$w^{-1}L =\{\epsilon,a,ab,\emptyset\} = \{\epsilon,a,ab\}$
	
	${(wa)}^{-1}L = {(baa)}^{-1}L = \{\emptyset,\epsilon,b,\emptyset\} = \{\epsilon,b\}$
	
	$a^{-1}(w^{-1}L) = a^{-1}\{\epsilon,a,ab\} = \{\emptyset,\epsilon,b\} = \{\epsilon,b\}$
	
	$w\in L \equiv \epsilon \in w^{-1}L,and {(wa)}^{-1}L = a^{-1}(w^{-1}L)$ \hfill$\square$ 
\end{example}

\begin{example}
	$a^{-1}\{a\} = \{\epsilon\}; \quad a^{-1}\{b\} = \emptyset,\quad\Leftarrow if (a\ne b)$ \hfill$\square$ 
\end{example}

\begin{example}
	$L_0 = \{ab\},L_1 = \{ac\}, L_0L_1 = \{abac\}$
	
	$a^{-1}(L_0L_1) = \{bac\}$
	
	$a^{-1}(L_0L_1) = (a^{-1}L_0)L_1 \cup \emptyset \quad \Leftarrow(\epsilon \notin L_0)$
	
	$= \{b\}L_1 = \{bac\}$ \hfill$\square$ 
\end{example}

\begin{example}
	$L_0 = \{\epsilon,ab\},L_1 = \{ac\}, L_0L_1 = \{ac,abac\}$
	
	$a^{-1}(L_0L_1) = \{c,bac\}$
	
	$a^{-1}(L_0L_1) = (a^{-1}L_0)L_1 \cup a^{-1}L_1 \quad\Leftarrow(\epsilon \in L_0)$
	
	$= \{\emptyset,b\}L_1 \cup \{c\} = \{c,bac\}$ \hfill$\square$ 
\end{example}

\begin{proof}
	$a^{-1}(L_0L_1)$
	
	$1. if(\epsilon \in L_0) \Rightarrow a^{-1}(L_0L_1) = (a^{-1}L_0)L_1 \cup a^{-1}L_1 $ 
	
	$L_0 = (L_0 \backslash \{\epsilon\}) \cup \{\epsilon\}$
	
	$a^{-1}(L_0L_1) = a^{-1}(((L_0 \backslash \{\epsilon\}) \cup \{\epsilon\})L_1)$
	
	$=a^{-1}(L_0L_1\cup L_1)$
	
	$a^{-1}L_0 = a^{-1}((L_0 \backslash \{\epsilon\}) \cup \{\epsilon\})$
	
	$=a^{-1}(L_0\ \backslash \{\epsilon \}) \cup a^{-1}\{\epsilon \}$
	
	$=a^{-1}L_0 \cup \emptyset = a^{-1}L_0$
\end{proof}
	

\clearpage

From \cite[p99]{Hopcroft2008}

(1)如果$L$是一个语言，$a$是一个符号，则$L/a$(称作$L$和$a$的商)是所有满足如下条件的串$w$的集合：$wa$属于$L$。
例如，如果$L=\{a,aab,baa\}$,则$L/a = \{\epsilon,ba\}$, 证明：如果$L$是正则的，那么$L/a$也是。提示：从$L$的$DFA$出发，考虑接受状态的集合。

(2)如果$L$是一个语言，$a$是一个符号，则$a\backslash L$是所有满足如下条件的串$w$的集合: $aw$属于$L$。例如，如果$L=\{a,aab,baa\}$,则$a\backslash L=\{\epsilon,ab\}$,证明：如果$L$是正则的，那么$a\backslash L$也是。提示：记得正则语言在反转运算下是封闭的，又由(1)知，正则语言的商运算下是封闭的。

\begin{definition}[Kleene-closure\cite{Chrison2007}]
	Let $L\subseteq V^{\ast}$, then 
	$$L^{\ast} := \{\epsilon\}\cup L \cup LL\cup LLL\cup \cdots$$ 
\end{definition}

This is the same operation that we defined above for the set V, except that now it is applied to set L whose elements may be strings of length greater than one. An element of $L^*$ is formed by the concatenation of a finite (but possibly arbitrarily large) number of elements of L; this includes the concatenation of "zero" elements, that is the empty string $\epsilon$. Note that $\ast$ operation is idempotent: ${(L^*)}^* = L^*$.
\begin{align*}
L^{\ast} &= \{\epsilon\} +L^{+} \\
&=  \{\epsilon\}\cup (L\backslash \{\epsilon\})L^{\ast}\\ &=\{\epsilon\} + L + LL + LLL + \cdots 
\end{align*}

\section{Linear equation}

see \cite[5.3,p64]{Jean2018}.

We give an algorithm to covert an automaton to a rational(regular) expression. The algorithm amounts to solving a system of linear equations on languages. We first consider an equation of the form
\begin{equation}\label{Linear equation}
X = KX + L
\end{equation}

\begin{proposition}[Arden's Lemma]
	if $K$ does not contain the empty word, then $X = K^\star L$ is the unique solution of the equation $X = KX + L$.
\end{proposition}
where $K$ and $L$ are languages and $X$ is the unknown. When $K$ does not contain the empty word, the equation admits a unique solution.

\begin{proof}
	Replacing $X$ by $K^{\ast}L$ in the expression $KX+L$,one gets
	$$K(K^{\ast})L + L = K^{+}L + L = (K^{+}L + L) = K^{\ast}L,$$
	and hence $X = K^{\ast}L$ is a solution of (\ref{Linear equation}). see\footnote[1]{\begin{align*}
		K^{\ast} &= \{\epsilon\} + K^{+} \\
		&=  \{\epsilon\} + (K\backslash \{\epsilon\})K^{\ast}\\ &=\{\epsilon\} + K + KK + KKK + \cdots 
		\end{align*}}\label{star}
	
	To Prove uniqueness, consider two solutions $X_{1}$ and $X_{2}$ of (\ref{Linear equation}). By symmetry,it suffices to show that each word $u$ of $X_1$ also belongs to $X_2$. Let us prove this result by induction on the length of $u$.
	
	If $|u| = 0$, $u$ is the empty word\footnote[2]{The empty word = $\epsilon,|\epsilon| = 0$; if a language $M = \{\epsilon\}, |M| = 1$, The empty language $M = \emptyset, |M| = 0$. 文献\cite{Jean2018}用1表示$\epsilon$,因为$\epsilon K = K\epsilon = K$, 因此,$\epsilon$是连接运算的单位元，正是1表示的用意。0表示$\emptyset$,它是并运算的单位元,$K\cup \emptyset = \emptyset \cup K = K$.} and if $u \in X_1 = KX_1 + L$, then necessarily $u\in L$ since $\epsilon \notin K$. But in this case, $u\in KX_2 + L = X_2$. see\footnote[3]{In this case,$|u| = 0, X = \{\epsilon\},|X| = 1.\quad i.e.\quad\epsilon = K\epsilon + L, \epsilon = K + L$}
	
	For the induction step, consider a word $u$ of $X_1$ of length $n + 1$. Since $X_1 = KX_1 + L, u$ belongs either to $L$ or to $KX_1$. if $u\in L$, then $u\in KX_2 + L = X_2$. If $u\in KX_1$ then $u = kx$ for some $k\in K$ and $x\in X_1$. Since $k$ is not the empty word, one has necessarily $|x| \leq n$ and hence by induction $x\in X_2$.[see\footnote[4]{$u = kx,|u|=|kx|=n+1,\epsilon \notin K,|k|\ge 1,|x|\le n$,由假设知，$u$属于$X_1$,归纳$|x|=0,|x|=1,\cdots,n,x\in X_2$.}] It follows that $u\in KX_2$ and finally $u\in X_2$. This conclude the induction and the proof of the proposition.  \hfill$\square$ 
\end{proof}

\begin{svgraybox}
	
From \cite[p74]{Wonham2018} 
The \textit{length} $|s|$ of a string $s\in \Sigma^{\ast}$ is defined according to
$$|\epsilon| = 0; |s| = k, \text{if }s = \sigma_1\sigma_2 \cdots\sigma_k\in \Sigma ^{+}$$
Thus $|cat(s,t)| = |s| + |t|$.

A \textit{language} over $\Sigma$ is any subset of $\Sigma^{\ast}$, i.e. an element of the power set $Pwr(\Sigma^{\ast})$; thus the definition includes both the empty language $\emptyset$, and $\Sigma^{\ast}$ itself.

Note the distinction between $\emptyset$ (the language with no strings) and $\epsilon$ (the string with no symbols). For instance the language $\{\epsilon\}$ is nonempty, but contains only the empty string.
\end{svgraybox}	

From \cite[p78]{Wonham2018}
\begin{proposition}[\cite{Wonham2018}]
	\begin{enumerate}
		\item If $L = M^{\ast}N$ then $L = ML + N$
		\item If $\epsilon\notin M$ then $L = ML + N$ implies $L = M^{\ast}N$ \hfill$\square$ 
	\end{enumerate}
\end{proposition}
Part(2) is Known as Arden's rule. Taken with Part(1) it says that if $\epsilon\notin M$ then $L = M^{\ast}N$ is the unique solution of $L = ML + N$; in particular if $L = ML$ (with $\epsilon \notin M$) then $L = \emptyset$

\begin{exercise}
	Show by counterexample that the restriction $\epsilon \notin M$ in Arden's rule cannot be dropped.
\end{exercise}
\begin{solution}
	Examples text goes here.  
\end{solution}

\begin{exercise}
	Prove Arden's rule. Hint: If $L = ML + N$ then for every $k\geq 0$
	$$L = M^{k+1}L + (M^{k} + M^{k-1} + \cdots + M + \epsilon)N$$
\end{exercise}

\begin{solution}
	\begin{align*} Preliminaries:\\
		M^{\ast} &= M^{k} + M^{k-1} + \cdots + M^{1} + M^{0} \qquad (k\geq 0)\\
		         &= M^{k} + M^{k-1} + \cdots + M^{1} + \epsilon \\ 
		         &= M^{+} + \epsilon\\
		         &= MM^{*} + \epsilon\\
		         &= (M\backslash\{\epsilon\})M^{*} + \epsilon\\
		M^{+} &= M^{k} + M^{k-1} + \cdots + M^{1} \qquad (k > 0)\\
		      &= M(M^{k} + M^{k-1} + \cdots + M^{1} + M^{0}) \\ 
		      &= MM^{*}\\
	    M^{0} &= \{\epsilon\} = 1\\
	    M\epsilon &= \epsilon M = M\\
	    \epsilon+\epsilon &=\epsilon\\
	    M+M &= M
	\end{align*}
	\begin{proof}
		$$L = ML + N \Rightarrow$$  
		\begin{align}
			M^0L &= M^1L + M^0N \\
			M^1L &= M^2L + M^1N \\ 
			M^2L &= M^3L + M^2N \\ 
		\end{align}
		$$\cdots$$
		$\Rightarrow\\ (M^0+M^1+M^2+\cdots)L = (M^1+M^2+M^3+\cdots)L + (M^0+M^1+M^2+\cdots)N \\ \Rightarrow$ 
	    
	    so,if $L = ML +N$,then for every $k \ge 0$
	    
		$L = M^{k+1}L + (M^k+M^{k-1}+\cdots+M+M^0)N \\ \Rightarrow$
		
		\begin{equation}\label{leq}
			L = M^{k+1}L + (M^k+M^{k-1}+\cdots+M+\epsilon)N
		\end{equation}
		
		(1) $k = 0$\\
		$L = ML + (\epsilon)N = ML + N \\ \Rightarrow 
		(1-M)L = N \\
		(\epsilon-M)L = N$\\
		由于$\epsilon \notin M$,左端不会消去\{$\epsilon$\}.因此,只能在$N$中找$L$,仅有唯一解: $L
		=\{\epsilon\} = \text{\{empty word\}} \subseteq N$.  

	\end{proof}
%	Replacing L by $M^{\ast}N$ in the expression $ML + N$, one gets
%	\begin{align*}
%	     $L = ML + N$
%	\end{align*}
%	and hence $L = M^{*}N$ is a solution of $L = ML + N$. 
%	
%	To Prove uniqueness, consider two solutions $L_{1}$ and $L_{2}$ of $ML + N$. By symmetry,it suffices to show that each string $s$ of $L_1$ also belongs to $L_2$. Let us prove this result by induction on the length of $s$.
%	
%	if $|s| = 0$, $s$ is the empty string($\epsilon$) and if $s\in L_1 = ML_1 + N$, then necessarily $s\in N$ since $\epsilon\notin M$. But in this case, $s\in ML_2 + N = L_2$. see\footnote[1]{In this case,$|s| = 0, L = \{\epsilon\},|L| = 1.\quad i.e.\quad\epsilon = M\epsilon + N,  \epsilon = M + N$}
%	
%	Replacing L by $M^{\ast}N$ in the expression $ML + N$, one gets
%	\begin{align*}
%	L = M(M^{\ast}N) + N &= M((M^{k} + M^{k-1} + \cdots + M^{1} + M^{0})N) + N \qquad (k\geq 0)\\
%	&= \text{(by associative law)} \\ 
%	&= (M(M^{k} + M^{k-1} + \cdots + M^{1} + M^{0}))N + N \\
%	&= \text{(by distributive law)} \\ 
%	&= (M^{k+1} + M^{k} + M^{k-1} + \cdots + M^{1})N + N \\
%	&= \text{(by distributive law)} \\ 
%	&= M^{k+1}N + (M^{k} + M^{k-1} + \cdots + M^{1})N + N \\
%	&= M^{k+1}N + (M^{k} + M^{k-1} + \cdots + M^{1} + 1)N \\
%	&= \text{by }(M^{0} = \epsilon = 1) \\
%	&= M^{k+1}N + (M^{k} + M^{k-1} + \cdots + M^{1} + \epsilon)N \\
%	&= M^{k+1}N + M^{*}N \\
%	&= \text{(by $L = M^{*}N$)} \\
%	&= M^{k+1}N + L
%	\end{align*}  
%	$k\geq 0$
%	$$L = M^{k+1}L + (M^{k} + M^{k-1} + \cdots + M + \epsilon)N$$ 

\end{solution}

%\input{referenc}

\begin{thebibliography}{99}
	\bibitem[Hopcroft2008]{Hopcroft2008}
	John E. Hopcroft,Rajeev Motwani,Jeffrey D. Ullman著,孙家骕等译,\textit{自动机理论、语言和计算机导论},Third Edition, 机械工业出版社,2008.7
	
	\bibitem[WATSON93a]{WATSON93a}
	WATSON, B. W. \textit{A taxonomy of finite automata construction algorithms}, Computing Science Note 93/43, Eindhoven University of Technology, The Netherlands, 1993. Available by ftp from ftp.win.tue.nl in pub/techreports/pi.
	
	\bibitem[WATSON93b]{WATSON93b}
	WATSON, B. W. \textit{A taxonomy of finite automata minimization algorithms}, Computing Science Note 93/44, Eindhoven University of Technology, The Netherlands, 1993. Available by ftp from ftp.win.tue.nl in pub/techreports/pi.
	
	\bibitem[WATSON94a]{WATSON94a}
	WATSON, B. W. \textit{An introduction to the FIRE engine: A C++ toolkit for FInite automata and Regular Expressions}, Computing Science Note 94/21, Eindhoven University of Technology, The Netherlands, 1994. Available by ftp from ftp.win.tue.nl in pub/techreports/pi
	
	\bibitem[WATSON94b]{WATSON94b}
	WATSON, B.W. \textit{The design. and implementation of the FIRE engine:	A C++ toolkit for FInite automata and Regular Expressions}, Computing Science Note 94/22, Eindhoven University of Technology, The Netherlands, 1994. Available by ftp from ftp.win.tue.nl in pub/techreports/pi.
	
	\bibitem[Chrison2007]{Chrison2007}
	Christos G. Cassandras and St$\acute{e}$phane Lafortune, \textit{Introduction to Discrete Event Systems},Second Edition,New York,Springer,2007
	
	\bibitem[Wonham2018]{Wonham2018}
	W. M. Wonham and Kai Cai,\textit{Supervisory Control of Discrete-Event Systems}, Revised 2018.01.01
	
	\bibitem[Jean2018]{Jean2018}
	Jean-$\acute{E}$ric Pin, \textit{Mathematical Foundations of Automata Theory},Version of June 15,2018
	
	\bibitem[蒋宗礼2013]{蒋宗礼2013}
	蒋宗礼,姜守旭, \textit{形式语言与自动机理论（第3版）}, 清华大学出版社,2013.05
	
	
	\bibitem{Lipschutz2007}
	S. Lipschutz and M. L. Lipson, \textit{Schaum's Outline of Theory and Problems of Discrete Mathematics}, Third Edition, New York: McGraw-Hill, 2007.
	
	\bibitem{Rosen2007}
	K. H. Rosen, \textit{Discrete Mathematics and Its Applications}, Seventh Edition, New York: McGraw-Hill, 2007.
	
	\bibitem{Maclane1988}
	S. Maclane and G. Birkhoff, \textit{Algebra}, Third Edition, New York: Bchelsea Publishing Company, 1988.
\end{thebibliography}

